\huge A Usability Evaluation of Tor Launcher

### 2017-03-23 pets2017-paper/pets2017-paper.tex
minor additions for formatting

\subsection{Testing Pipeline} 
We began by performing a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons.
A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement.
We then conducted qualitative and quantitative usability tests.
We believe both methods were necessary for a complete usability evaluation.
Qualitative testing illuminates {\it why or how} the software is or is not usable, while quantitative testing measures {\it to what extent}.
We used our qualitative study observations to design interface changes that would address encountered issues.
We used quantitative testing to measure the impact of our proposed changes, as compared to the original interface.

@@

\subsection{Experimental Setup}
\label{sec:environments}
We chose to simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex. Re-routing participant traffic through other countries' networks also may introduce unforeseen risks to the participants out of our control and performing hundreds of connections in short intervals during experiments may draw unnecessary attention to Tor use in that country. The three environments are described in Table~\ref{tab:environments}.

\begin{table}[t]
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & X & X \\
public relays blocked & & X & X \\
default bridges blocked & & & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires users to connect directly;
E2 requires users to connect with a built-in bridge;
and E3 requires users to connect with a specific type of built-in bridge
or a custom bridge.
E2's blocking is a superset of E1's;
similarly, E3's is a superset of E2's.
}
\label{tab:environments}
\end{table}

>>>>

\subsection{Testing Pipeline} 
We began by performing a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons.
A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement.
We then conducted qualitative and quantitative usability tests.

Qualitative testing is used to gain an understanding of underlying reasons, opinions, and motivations. We use qualitative testing to develop hypotheses about why people struggle to use the interface and devlop ideas for potential design modifications to the interface.

Quantitative testing is used to quantify the problem by way of generating numerical data or data that can be transformed into useable statistics. We use quantitative testing to quantify how people interact with the interface to uncover user patterns.

We believe both methods were necessary for a complete usability evaluation.
Qualitative testing illuminates {\it why or how} the software is or is not usable, while quantitative testing measures {\it to what extent}.
We used our qualitative study observations to design interface changes that would address encountered issues.
We used quantitative testing to measure the impact of our proposed changes, as compared to the original interface.

@@

\subsection{Experimental Setup}
\label{sec:environments}
We chose to simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex. Re-routing participant traffic through other countries' networks also may introduce unforeseen risks to the participants out of our control and performing hundreds of connections in short intervals during experiments may draw unnecessary attention to Tor use in that country. The three simulated censorship environments, which we refer to as E1, E2, and E3 throughout the paper, are summarized in Table~\ref{tab:environments}. E2's censorship is a superset of E1's; similarly, E3's censorship is a superset of E2's.

\begin{table}[t]
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & X & X \\
public relays blocked & & X & X \\
default bridges blocked & & & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires users to connect directly;
E2 requires users to connect with a built-in bridge;
and E3 requires users to connect with a specific type of built-in bridge
or a custom bridge.
}
\label{tab:environments}
\end{table}
